% Auto-generated captions for figures.

% --- fig1_sector_diagram ---
\caption{Same-\(i\) sector geometry. Fixed local complex structures \(J_A,J_B\) define \(M=J_A\otimes J_B\) on the full real tensor product \(K_{AB}\). The aligned sector \(H_+=\ker(M+I)\) represents the realified ordinary complex tensor product, while \(H_-=\ker(M-I)\) is the leakage sector. Ordinary complex quantum theory also requires \(J_{AB}\)-compatible states and effects inside \(H_+\).}

% --- fig2_cfr_leakage ---
\caption{Leakage of the Caves--Fuchs--Rungta two-rebit family. With \(J_A=J_B=i\sigma_y\), one has \(M=-\sigma_y\otimes\sigma_y\) and \(\rho_{\rm CFR}(\alpha)=\tfrac14(I-\alpha M)\), so \(L(\rho_{\rm CFR}(\alpha))=(1-\alpha)/2\). The family is block diagonal in \(H_+\oplus H_-\), hence its coherent leakage \(C\) vanishes for all \(\alpha\).}

% --- fig3_coherent_leakage_bound ---
\caption{Population leakage \(L(\rho)\) and coherent leakage \(C(\rho)=\|P_+\rho P_-\|_1\). The solid curve is the sharp bound \(C\le\sqrt{L(1-L)}\). Coherent pure cross-sector states saturate the bound, while block-diagonal states have \(C=0\) for every value of \(L\). Random real density operators lie below the envelope.}

% --- fig4_sector_parity_discrimination ---
\caption{Optimal success probability for the internal sector-parity discrimination primitive. The advantage is controlled by coherent cross-sector amplitude: coherent probes attain \(p_{\rm succ}^{(\epsilon)}=\tfrac12+\sqrt{m(1-m)}\), \(m=\min\{\epsilon,1/2\}\), while block-diagonal probes remain at \(p_{\rm succ}=\tfrac12\).}

% --- fig5_perturbative_leakage ---
\caption{Numerical sanity check for perturbative leakage generation. Starting from an aligned state and a sector-preserving generator \(G_0\), a skew perturbation \(B\) with cross-sector component generates leakage at second order: \(L=\epsilon^2\|a(t)\|^2+O(\epsilon^3)\). The fitted log--log slope is reported in the reproducibility file. This plot is illustrative; the proof is given analytically.}

